TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
minor

\tableofcontents
\todoi{Comparison with hammers in usability}

@@

\todoi{Rewrite the plan}
  To do this, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for a \emph{Monte Carlo tree search} that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a certified human-level proof composed of \holfour
  tactics.  The system is evaluated on a large set of theorems originating
  from \holfour (Section~\ref{s:experiments}), and we show that the performance
  of the single best \tactictoe strategy exceeds the performance of a hammer
  system used with a single strategy and a single efficient external prover.

>>>>

\tableofcontents
\todoi{Comparison with hammers in usability, easier reconstruction nice proofs}

@@

\todoi{Rewrite the plan}
  To do this, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for a \emph{Monte Carlo tree search} that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a certified human-level proof composed of \holfour
  tactics.  The system is evaluated on a large set of theorems originating
  from \holfour (Section~\ref{s:experiments}).
